\bf Measuring background and systemic risk using financial time series

### 2015-06-04 srisk6.tex
pdj changes

\documentclass[authoryear]{elsarticle}
\usepackage{latexsym}
%\usepackage{rotate}
\usepackage{graphics}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{comment}
\bibliographystyle{chicago}

\makeatletter
\def\ps@pprintTitle{%
\let\@oddhead\@empty
\let\@evenhead\@empty
\def\@oddfoot{}%
\let\@evenfoot\@oddfoot}
\makeatother

@@

% Title of paper
\title{Measuring background and systemic risks in finance}
% List of authors, with corresponding author marked by asterisk
\author{Piet de Jong,  Geoffrey loudon and Weihao Choo \\[4pt]
% Author addresses
\textit{Department of Applied Finance and Actuarial Studies\\ Macquarie University, Sydney, NSW 2109.}
\\[2pt]
%E-mail address for correspondence
{piet.dejong@mq.edu.au}}

% Running headers of paper:
\markboth%
% First field is the short list of authors
{De Jong}
% Second field is the short title of the paper
{Systemic risk}

\begin{abstract}
This article refines, builds on, and extends the systemic risk methodology [SRISK] recently proposed by \cite{brownlees2015}. We refine SRISK by defining it in terms of a put on the Basel shortfall. We build on this by distinguishing background and systemic stress of a firm. Background stress is the unconditional expectation of the put. Systemic stress is the departure from the unconditional expectation when a hypothetical systemic stress is applied.  Systemic stress is defined in terms of a random variable and can take on variety of forms including alternative scenarios as in usual stress testing and also 
stress driven by the interaction of variables. Stressor random variables are chosen by the practitioner. Stressed expectations are linear and sector systemic stress is naturally defined as linear in the firm specific systemic stress. Application is made to Australian financial data.
\end{abstract}

\maketitle

JEL classification
C15; E53; G21  %(Needs to be filled out)

\section{Introduction}

Monitoring systemic risk is a key function of macro-prudential regulation. Central banks and other financial regulatory bodies such as the US Financial Stability Oversight Council, the European Systemic Risk Board and the Australian Prudential Regulation Authority [APRA] are concerned with developing and applying quantitative risk measures to alert them of potential episodes of heightened systemic risk. Systemic risk has many dimensions. For example, in their influential review paper, \cite{Bisias2012} present a taxonomy of six categories of systemic risk comprising 31 quantitative risk measures. While attempts to gain consensus on a theoretical definition have proved elusive, several empirical measures of systemic risk have been developed and applied with some success.  An important example is the SRISK measure due to \cite{brownlees2015} which proposes an index that measures the expected capital shortfall on a financial institution conditional on a large and lengthy decline in equity markets. \cite{brownlees2015} show the practical usefulness of their measure in three ways: (i) SRISK rankings identify systemically risky US banks during the global financial crisis [GFC]; (ii) pre-crisis SRISK helps predict capital injections by the Fed Reserve; (iii) aggregate SRISK provides early warning of declines in industrial production and higher unemployment.

Our paper builds upon and extends the model of \cite{brownlees2015} in several interesting and important ways. First, we reinterpret their SRISK measure as a put on the expected shortfall using stressed expectation. While they condition on the event of a severe market downturn, we take the stressed expectation of the put value. This enables us to capture the impact of increased return volatility due to stress. Second, we decompose their SRISK measure into background stress and imposed system stress. Background stress is a function of existing volatility and leverage. As these factors increase, background stress rises and this makes the firm more susceptible to systemic risk, regardless of the stress event itself. Third,    
\cite{brownlees2015} condition on an absolute cutoff of arbitrary size and length. We suggest that it is also helpful to specify conditional behaviour in percentile terms relative to current market conditions. This provides a sharper focus on the incremental impact of further stress and allows us to draw stronger implications of SRISK numbers. These extensions provide additional insights into the sources and economic nature of systemic risk. They provide potentially new and improved ways of anticipating episodes of heightened systemic risk. Their practical use can be expected to help regulators monitor systemic risk in a timely fashion to facilitate remedial action where necessary.

@@

Remaining sections are structured as follows. \sref{litrev} briefly discusses some related literature. \sref{capshort} and \sref{futshort} define current and future  capital shortfall similarly as \cite{brownlees2015} under a simplistic Basel II regulatory framework. The definition of systemic risk used by \cite{brownlees2015} is discussed in \sref{srisk}, and is refined, extended and illustrated \sref{improve} to \sref{estimate}. \sref{marketstress} discusses specific stress examples which extend beyond \cite{brownlees2015}. Applications to Australian bank data are discussed in \sref{simulate} and \sref{simulate1}. \sref{aggregate} and \sref{aggregate1} discuss how stresses are combined across firms with and without allowance for merging or diversification. Generalised stressed are outlined in \sref{genstress}. \sref{riskmethod} offers an alternative modeling approach, based on assets. \sref{comparison} summarises differences between proposed stress measurement in this paper with that of 
\cite{brownlees2015}. \sref{conclude} concludes.

\begin{table}[htdp]
\label{banks}\caption{Major and minor Australian banks}\label{eightbanks}
\begin{center}
\begin{tabular}{l|l||l|l}
\hline
 \multicolumn{2}{c||}{major}& \multicolumn{2}{c}{minor}\\
 \hline
cba & Commonwealth Bank  & mqg & Macquarie \\
anz & Australia \& New Zealand  & boq & Bank of Queensland\\
nab & National Australia  & ben & Bendigo and Adelaide \\
wbc & Westpac & aba & Auswide \\
\hline
\end{tabular}
\end{center}
\end{table}%

\begin{figure}[htbp]
\begin{center}
\includegraphics{figures/prices.pdf}
\caption{Stock  prices of four major (left panel) and four minor (right panel) Australian banks from early 2000 through to the end of 2014.  All prices normalised to start at 1.}
\label{prices}
\end{center}
\end{figure}

@@

The genesis of SRISK lies in a series of papers including \cite{acharya2012capital}, \cite{acharya2012measuring} and \cite{brownlees2010volatility}. In these papers, SRISK is defined as the expected capital shortfall of a financial firm, conditional on a crisis. A crisis is deemed to occur whenever the relevant market index suffers a significant decline over a chosen horizon. \cite{Benoit2013} show how several popular systemic risk measures including MES and SRISK are transformations of market risk measures and derive conditions under which these measures provide similar rankings of systemically important financial institutions.

@@

Empirical estimates of SRISK measure require a model for the joint distribution of returns of individual firms and the market. Many of these papers use \cite{engle2002dynamic}'s GARCH-DCC model which nicely captures the time-varying dynamics of the return (co)variances in a feasible manner. While we also use this model in our empirical analysis, we emphasize that our approach can utilise any appropriate model for simulating forward the joint distribution of firm and market returns.

@@

The capital  shortfall  at time $t+h$, ignoring the surplus portion, is,
\be{bs}
\kappa d_{it} \left|1-\e^{-\ell_{i,t+h}}\right|^+=\kappa d_{it} \left|1-\e^{\nu_{it}-\ell_{it}}\right|^+
\cq  |x|^+\equiv \max(0,x)\ .
\ee
Thus shortfall \eref{bs} is a $\kappa d_{it}$ multiplied by a put on the return $\e^{\nu_{it}-\ell_{it}}$  with strike 1.
The Basel  limit is reached at $t+h$ if $\nu_{it}=\ell_{it}$ and  breached  if
$\nu_{it}< \ell_{it}$.
A breach is  unlikely if $\ell_{it}$ is low i.e. either the log--leverage or prudential requirement $\kappa$ is low. This paper models future capital shortfall using log return on equity $\nu_{it}$ as it is typically available publicly. An alternative approach models future asset values $d_{i,t+h}+w_{i,t+h}$ in turn implying equity returns, and is briefly discussed in \sref{riskmethod}. Results in this paper generally hold for any modeling approach.

@@

 The black dots in each panel indicate the actual outcome after one month.    In the left panel the outcome is a decline in both  the market and CBA stock price.    In the right panel the returns are xxx and xxx.    Thus at the beginning of January  2009 CBA was projected to be far from compliance in a month while in December 2014 the one month projection is of complete compliance.

@@

 \cite{brownlees2015} defines  systemic risk (SRISK) for a group of firms  at time $t$ as
\be{esrisk}
\mathrm{SRISK}_t\equiv\kappa\sum_i d_{it}\left|1-\Es(\e^{\nu_{it}-\ell_{it}})\right|^+ \ ,
\ee
where  $\Es$ denotes expectation given a major general market downturn. Hence the expected capital shortfall (allowing surplus offset) is computed from \eref{shortfall} assuming a market downturn and added across all firms. Firms having an expected capital surplus are ignored. The systemic risk of firm $i$ at time $t$ is its proportionate contribution to \eref{esrisk}:
 \be{sriskperc}
 \mathrm{SRISK}_{it}\equiv \pi_{it}\frac{|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+}{\Ex_d\{|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+\}}\cq \pi_{it}\equiv \frac{d_{it}}{d_t}\cq d_t\equiv \sum_i d_{it}\ ,
 \ee
where $\Ex_d$ denotes weighted averaging across firms $i$ using weights $\pi_{it}$.     Large $\mathrm{SRISK}_{it}$ indicates firm $i$ is systemically important: it holds a high proportion of the total debt, and it is likely to heavily breach the Basel capital requirement compared to remaining other firms.  Expression \eref{sriskperc} depends on $\kappa$ through each of the $\ell_{it}$.

@@

Using the Jensen's inequality,
$$
\left|1-\Es(\e^{\nu_{it}-\ell_{it}})\right|^+ \le\Es\left(\left|1-\e^{\nu_{it}-\ell_{it}}\right|^+\right)\ ,
$$
with equality  if  $\nu_{it}-\ell_{it}$ is concentrated on the negative axis.  If  $\nu_{it}>\ell_{it}$  has positive probability then the  inequality is strict.   Further $\mathrm{SRISK}_{it}$ in \eref{sriskperc}   is zero whenever
$$
\Es(\e^{\nu_{it}})\ge\e^{\ell_{it}}\ .
$$
This inequality typically holds even if the expectation conditions on an extreme market downturn. The above two inequalities suggest SRISK is not risk sensitive and leads to refinements discussed in the next section.

@@

The above two situations can be combined.   Suppose  $\phi(u)=c(\alpha-u)^{n-1}$ for $u\le \alpha$ and 0 otherwise and where $c$ is such that $\phi(u)$ integrates to 1. Then
$$
\mu_{it}+s_{it} \approx \frac{1}{N/c}\sum_{u^\o_{mt}<\alpha}  \left(\alpha-u^\o_{mt}\right)^{n-1}p_{it}^\o\ .
$$
Similar to the first example, the stressed sample picks up the bottom $\alpha$ of market returns. The bottom $\alpha$ of market returns is further stressed by  progressively overweighing returns as the percentile approaches 0.   Large simulation effort $N$ is required for a reasonable approximation since $N/c$ is the effective simulation size and $c$ is small.

\section{Simulating future capital shortfall and market return}\label{simulation}

@@

\section{One month ahead forecast stresses in individual banks}\label{simulate1}

@@

@@

 \section{Further generalised stress functions}\label{genstress}

@@

\newpage

@@

Can easily determine all terms via simulation.

@@

\section*{References}
\bibliography{piet2}

\end{document}

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf,comment}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL 
\bibliographystyle{chicago}

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%

@@

%\bibliographystyle{natbib}

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\if0\blind
{
  \title{\bf Measuring background and systemic risk using financial time series}
  \author{Piet de Jong\thanks{
    The authors gratefully acknowledge CIFR, the Centre of International Financial Regulation for financial support and other assistance.}\hspace{.2cm}\\
    Department of Applied Finance and Actuarial Studies, Macquarie University\\
    and \\
    Geoff Loudon\\
    Department of Applied Finance and Actuarial Studies, Macquarie University\\
    and\\
    Weihao Choo\\
    Department of Applied Finance and Actuarial Studies, Macquarie University}
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Title}
\end{center}
  \medskip
} \fi

\bigskip
\begin{abstract}
This article refines and extends  SRISK methodology recently proposed in the literature.  The refinement is to define systemic risk in terms of a put on the Basel shortfall.  Background and systemic stress  of a firm are defined as unconditional, and departure from unconditional  expectation, of the put, the latter when a hypothetical systemic stress is applied.  Systemic stress is defined in terms of a random variable and can take on variety of forms including alternative scenarios in usual stress testing as well stress driven by the interaction of variables.  Stressor random variables  are chosen by the practitioner.  Stressed expectations are linear, a sector systemic stress is naturally defined as linear in the firm specific systemic stress.      Application is made to Australian financial daily time series data.
\end{abstract}

\noindent%
{\it Keywords:}  3 to 6 keywords, that do not appear in the title
\vfill

\newpage
\spacingset{1.45} % DON'T change the spacing!

Monitoring stresses and systemic risk in the financial system is a key function of macro--prudential regulation. Central banks and other financial regulatory bodies such as the US Financial Stability Oversight Council, the European Systemic Risk Board and the Australian Prudential Regulation Authority [APRA] are concerned with developing and applying early warning quantitative  measures  to warn of potential episodes of heightened systemic risk. Systemic risk has many dimensions. For example, in their influential review paper, \cite{Bisias2012} present a taxonomy of six categories of systemic risk comprising 31 quantitative risk measures. While attempts to gain consensus on a theoretical definition have proved elusive, several empirical measures of systemic risk have been developed and applied with  success.  An important example is the SRISK measure due to \cite{brownlees2015} -- an index that measures the expected capital shortfall of a financial institution conditional on a large and lengthy decline in equity markets. \cite{brownlees2015} show the practical usefulness of their measure in three ways: (i) SRISK rankings identify systemically risky US banks during the global financial crisis [GFC]; (ii) pre-crisis SRISK helps predict capital injections by the Fed Reserve; (iii) aggregate SRISK provides early warning of declines in industrial production and higher unemployment.

Our paper refines and extends the model of \cite{brownlees2015} in several interesting and important ways. First, we reinterpret their SRISK measure as a put on the expected shortfall using stressed expectation. While they condition on the event of a severe market downturn, we take the stressed expectation of the put value. This eNABles us to capture the impact of increased return volatility due to stress. Second, we decompose their SRISK measure into background stress and imposed system stress. Background stress is a function of existing volatility and leverage. As these factors increase, background stress rises and this makes the firm more susceptible to systemic risk, regardless of the stress event itself. Third,    
\cite{brownlees2015} condition on an absolute cutoff of arbitrary size and length. We suggest that it is also helpful to specify conditional behaviour in percentile terms relative to current market conditions. This provides a sharper focus on the incremental impact of further stress and allows us to draw stronger implications of SRISK numbers. These extensions provide additional insights into the sources and economic nature of systemic risk. They provide potentially new and improved ways of anticipating episodes of heightened systemic risk. Their practical use can be expected to help regulators monitor systemic risk in a timely fashion to facilitate remedial action where necessary.

@@

Remaining sections are structured as follows. Section \ref{litrev} briefly discusses some related literature. Section \ref{capshort} and \ref{futshort} define current and future  capital shortfall similarly as \cite{brownlees2015} under a simplistic Basel II regulatory framework. The definition of systemic risk used by \cite{brownlees2015} is discussed in \sref{srisk}, and is refined, extended and illustrated \sref{improve} to \sref{estimate}. Section \ref{marketstress} discusses specific stress examples which extend beyond \cite{brownlees2015}. Applications to Australian bank data are discussed in \sref{simulate} and \sref{simulate1}. Section \ref{aggregate} and \ref{aggregate1} discuss how stresses are combined across firms with and without allowance for merging or diversification. Section \ref{monitoring} displays system stress calculations as they would proceed in real time. Generalised stresses are outlined in \sref{genstress}.  Section \ref{riskmethod} offers an alternative modelling approach, based on assets. Section \ref{comparison} summarises differences between proposed stress measurement in this paper with that of 
\cite{brownlees2015}. Section \ref{conclude} concludes.

\begin{table}[htdp]
\label{banks}\caption{Major and minor Australian banks}\label{eightbanks}
\begin{center}
\begin{tabular}{l|l||l|l}
\hline
 \multicolumn{2}{c||}{major}& \multicolumn{2}{c}{minor}\\
 \hline
CBA & Commonwealth Bank  & MQG & Macquarie \\
ANZ & Australia \& New Zealand  & BOQ & Bank of Queensland\\
NAB & National Australia  & BEN & Bendigo and Adelaide \\
WBC & Westpac & ABA& Auswide \\
\hline
\end{tabular}
\end{center}
\end{table}%

\begin{figure}[htbp]
\begin{center}
\includegraphics{figures/prices.pdf}
\caption{Stock  prices of four major (left panel) and four minor (right panel) Australian banks from early 2000 through to the end of 2014.  Price series normalised to start at 1.}
\label{prices}
\end{center}
\end{figure}

@@

The genesis of SRISK lies in a series of papers including \cite{acharya2012capital}, \cite{acharya2012measuring} and \cite{brownlees2010volatility}. In these papers, SRISK is defined as the expected capital shortfall of a financial firm, conditional on a crisis. A crisis is deemed to occur whenever a relevant market index suffers a significant decline over a chosen horizon. \cite{Benoit2013} show how several popular systemic risk measures including MES and SRISK are transformations of market risk measures and derive conditions under which these measures provide similar rankings of systemically important financial institutions.

@@

Empirical estimates of SRISK measure require a model for the joint distribution of returns of individual firms and the market. Many of these papers use \cite{engle2002dynamic}'s GARCH-DCC model aiming to capture the time-varying dynamics of the return (co)variances in a feasible manner. While we also use this model in our empirical analysis, we emphasize that our approach can utilise any appropriate model for simulating the joint distribution of forward firm and market returns.

@@

The capital  shortfall  at time $t+h$, ignoring the surplus portion, is,
\be{bs}
\kappa d_{it} \left|1-\e^{-\ell_{i,t+h}}\right|^+=\kappa d_{it} \left|1-\e^{\nu_{it}-\ell_{it}}\right|^+
\cq  |x|^+\equiv \max(0,x)\ .
\ee
Thus shortfall \eref{bs} is a $\kappa d_{it}$ multiplied by a put on the return $\e^{\nu_{it}-\ell_{it}}$  with strike 1.
The Basel  limit is reached at $t+h$ if $\nu_{it}=\ell_{it}$ and  breached  if
$\nu_{it}< \ell_{it}$.
A breach is  unlikely if $\ell_{it}$ is low i.e. either the log--leverage or prudential requirement $\kappa$ is low. This paper models future capital shortfall using log return on equity $\nu_{it}$ as it is typically available publicly. An alternative approach models future asset values $d_{i,t+h}+w_{i,t+h}$ in turn implying equity returns, and is briefly discussed in \sref{riskmethod}. The risk measurement approach of this paper can be combined with any forecasting approach.

@@

 The black dots in each panel indicate the actual outcome after one month.    In the left panel the outcome is a decline in both  the market and CBA stock price.    In the right panel there is slight decline in the stock price, and a more substantial market downturn.    Thus at the beginning of January  2009 CBA was projected to be far from compliance in a month while in December 2014 the one month projection is of complete compliance.

@@

 \cite{brownlees2015} defines  systemic risk (SRISK) for a group of firms  at time $t$ as
\be{esrisk}
\mathrm{SRISK}_t\equiv\kappa\sum_i d_{it}\left|1-\Es(\e^{\nu_{it}-\ell_{it}})\right|^+ \ ,
\ee
where  $\Es$ denotes expectation given a major general market downturn. Hence the expected capital shortfall (allowing surplus offset) is computed from \eref{shortfall} assuming a market downturn and added across all firms. Firms having an expected capital surplus are ignored. The systemic risk of firm $i$ at time $t$ is its proportionate contribution to \eref{esrisk}:
 \be{sriskperc}
 \mathrm{SRISK}_{it}\equiv \frac{\pi_{it}|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+}{\Ex_d\{|1-\Es(\e^{\nu_{it}-\ell_{it}})|^+\}}\cq \pi_{it}\equiv \frac{d_{it}}{d_t}\cq d_t\equiv \sum_i d_{it}\ ,
 \ee
where $\Ex_d$ denotes weighted averaging across firms $i$ using weights $\pi_{it}$.     Large $\mathrm{SRISK}_{it}$ indicates firm $i$ is systemically important: it holds a high proportion of the total debt, and it is likely to heavily breach the Basel capital requirement compared to remaining other firms.  Expression \eref{sriskperc} depends on $\kappa$ through each of the $\ell_{it}$.

@@

From Jensen's inequality,
$$
\left|1-\Es(\e^{\nu_{it}-\ell_{it}})\right|^+ \le\Es\left(\left|1-\e^{\nu_{it}-\ell_{it}}\right|^+\right)\ ,
$$
with equality  if  $\nu_{it}-\ell_{it}$ is concentrated on the negative axis.  If  $\nu_{it}>\ell_{it}$  has positive probability then the  inequality is strict.   Further $\mathrm{SRISK}_{it}$ in \eref{sriskperc}   is zero whenever
$$
\Es(\e^{\nu_{it}})\ge\e^{\ell_{it}}\ .
$$
This inequality typically holds even if the expectation conditions on an extreme market downturn. The above two inequalities suggest SRISK is not risk sensitive and leads to refinements discussed in the next section.

@@

The above two situations can be combined.   Suppose  $\phi(u)=c(\alpha-u)^{n-1}$ for $u\le \alpha$ and 0 otherwise and where $c$ is such that $\phi(u)$ integrates to 1. Then
$$
\mu_{it}+s_{it} \approx \frac{1}{N/c}\sum_{u^\o_{mt}<\alpha}  \left(\alpha-u^\o_{mt}\right)^{n-1}p_{it}^\o\ .
$$
Similar to the first example, the stressed sample picks up the bottom $\alpha$ of market returns. The bottom $\alpha$ of market returns is further stressed by  progressively overweighing returns as the percentile approaches 0.   Large simulation effort $N$ is required for a reasoNABle approximation since $N/c$ is the effective simulation size and $c$ is small.

\section{Simulating future capital shortfall and market return}\label{simulate}

@@

\section{One month ahead forecast stress in individual banks}\label{simulate1}

@@

\section{Month to month monitoring  of financial stress}\label{monitoring}
 \tref{twodates} contains real time stress calculations on the first trading day of  January 2009 and November 2014.  As before there is no look ahead bias -- all calculations on each of the two dates only use data available on the first day of the applicable month.   The initial eight rows in \tref{twodates} lists the eight banks used in this study.

 \begin{table}[ht]
\caption{One month ahead bank stress calculations$^\dag$}\label{twodates}
\centering
\small
\vspace{4mm}
\begin{tabular}{l|rrrrr|rrrrr}
\hline
&\multicolumn{5}{c|}{January 2009}&\multicolumn{5}{c}{November 2014}\\
  \hline
bank & B-log& debt &\multicolumn{2}{c}{stress}&  B-def   & B-log& debt   & \multicolumn{2}{c}{stress}& B-def \\
  \cline{4-5}\cline{9-10}
       &  lev& prop    & back & syst & prob & lev& prop  & back & syst & prob \\
  \cline{2-11} 
         & $\ell_{it} $ & $\pi_{it}$ & $\mu^*_{it}$  & $s^*_{it}$ & $q_{it}$  
         & $\ell_{it} $ & $\pi_{it}$ & $\mu^*_{it}$  & $s^*_{it}$ & $q_{it}$  
        \\
  \hline
CBA & 18.57 & 24.30 & 22.99 & 29.60 & 91.43 & -70.34 & 22.70 & 0.00 & 0.00 & 0.00 \\ 
  ANZ & 15.93 & 18.37 & 14.87 & 18.89 & 92.82 & -38.64 & 22.10 & 0.00 & 0.00 & 0.00 \\ 
  NAB & 31.97 & 25.50 & 39.98 & 19.41 & 99.97 & -12.45 & 25.61 & 50.52 & 67.13 & 1.23 \\ 
  WBC & -1.55 & 22.84 & 5.86 & 23.94 & 40.42 & -53.84 & 22.03 & 0.00 & 0.00 & 0.00 \\ 
  MQG & 41.22 & 5.75 & 11.02 & 5.46 & 99.92 & -46.10 & 4.33 & 0.17 & 0.12 & 0.03 \\ 
  BOQ & 63.30 & 1.32 & 3.55 & 0.99 & 99.95 & -17.05 & 1.33 & 0.80 & 1.34 & 0.33 \\ 
  BEN & 18.91 & 1.81 & 1.72 & 1.71 & 90.53 & -7.63 & 1.84 & 25.43 & 30.71 & 8.47 \\ 
  ABA& -8.12 & 0.10 & 0.00 & 0.00 & 9.97 & 9.22 & 0.07 & 23.07 & 0.71 & 89.63 \\ 
  \hline
  $\Ex_d$ & 18.78 &  & 17.17 & 8.63 & 82.72 & -41.91 &  & 0.03 & 0.12 & 0.54 \\ 
  $\Sigma$ & 17.81 & $^\dag$2.42 & 15.28 & 10.18 & 96.72 & -44.22 & $^\dag$3.27 & 0.00 & 0.00 & 0.00 \\ 
\hline
\end{tabular}

$^\dag$All numbers multiplied by 100 except total debt (in \$bln).
\end{table}
\normalsize

January 2009 was a time of great stress for all eight banks.     The first  and second columns in the two halves of the table body contain the 
 Basel log--leverage $\ell_{it}$ and debt $\pi_{it}\equiv d_{it}/d_t$ (as a proportion of total debt) for each of the banks.  Six of the eight banks were in Basel default with positive capital shortfalls as indicated in by the $\ell_{it}$ column:   the two banks not in Basel default were WBC and aba.    Background and systemic stress
$$
\mu^*_{it} \equiv \frac{\pi_{it}\mu_{it}}{\Ex_d(\mu_{it})}\cq s^*_{it} \equiv \frac{\pi_{it}s_{it}}{\Ex_d(\mu_{it})}\ , 
$$
for the banks as well as the probability of a Basel default in one month $q_{it}$ and the proportion $\pi_{it}$ of total debt are displayed in the next 3 columns.    The background stress column indicates most of the background stress arises from NAB -- almost 40\% of the total.   The next most background stressed bank is CBA with WBC also a substantial contributor.   The MQG bank contributes almost double to background stress compared to the proportion of total debt  it carries.  The other three small banks contribute relatively little to background stress with BOQ  almost 3 times expected on the basis of its debt.   Systemic stress is highest for the CBA, higher than expected on the basis of its debt load and hence CBA was most susceptible to stress from additional general market equity devaluation.    All other banks appear have systemic stress comparable to their size in terms of debt load with only NAB being less systemically important.    This should be compared to NAB's high background stress.

Continuing with January 2009, the final two rows indicate the total amount of stress in the system and it's diversifiability.    
The second last  row labelled $\Ex_d$  displays, in order, $\Ex_d(\ell_{it})$, blank, $\overline{\mu}_t\equiv \Ex_d(\mu_{it})$, $\overline{s}_t\equiv\Ex_d(s_{it})$ and  $\Ex_d(q_{it})$.   The final row labelled $\Sigma$ displays the aggregate stress quantities,treating all eight banks as one entity, $\ell_t$, total debt $d_t$ in billions of dollars,  $\mu_t$, $s_t$, and  $q_t$.
On an aggregate basis background stress is about twice systemic stress.   Thus there is more danger of increasing capital shortfall due to market volatility  as opposed to further stress from further substantial general market devaluation.  The final row indicates stresses are not diversifiable:    The marginally  smaller  ``diversified"  background stress is offset by an increase in systemic stress.    Also the diversified probability of Basel default is higher than the debt weighted average.

Stress readings  alter dramatically when moving to November 2014 -- there is virtually no stress in any bank and the small amount of  stress in the system is diversifiable.    Most of the  background stress is carried by NAB with lesser contributions by BEN and aba.    All the stress in the minor bank ABAis background stress as only NAB and NAB have substantial systemic stress contributions.   Again, however, it must be emphasised that there is minimal systemic stress in the system.    Only ABAhas substantial Basel default probability, but this bank is a small player in the Australian banking scene.   Notice total debt in the banking sector  jumps about 35\% between the two dates.

@@

 \section{Generalised stress functions}\label{genstress}

@@

\bigskip
\begin{center}
{\large\bf SUPPLEMENTARY MATERIAL}
\end{center}

@@

@@

\section{Submission guidelines}

\begin{itemize}
\item In the latex source, near the top of the file the command
\verb+\newcommand{\blind}{1}+ can be used to hide the authors and
acknowledgements, producing the required blinded version.
\item If you have supplementary material (e.g., software, data, technical
proofs), identify them in the section below.  In early stages of the
submission process, you may be unsure what to include as supplementary
material.  Don't worry---this is something that can be worked out at later stages.
\end{itemize}

\begin{description}

\item[Title:] Brief description. (file type)

\item[R-package for  MYNEW routine:] R-package ÒMYNEWÓ containing code to perform the diagnostic methods described in the article. The package also contains all datasets used as examples in the article. (GNU zipped tar file)

\item[HIV data set:] Data set used in the illustration of MYNEW method in Section~ 3.2. (.txt file)

\end{description}

\bibliography{piet2}
\end{document}
